Dependently Typed Languages in Statix

### 2023-04-24 pres-thesis/presentation.tex
Minor changes to the presentation
Change conclusion a bit

@@

\begin{frame}[fragile]{Extra contributions}
	% Refer to thesis for this
Features
\begin{enumerate}
	\item Implemented Inference
	\item Implemented Inductive Data Types
	\item Implemented Universes
	\item Interpreter
	\item Compiler to Clojure
\end{enumerate}
Evaluation
\begin{enumerate}
	\item Comparison with implementation in Haskell
	\item Comparison with implementation in LambdaPi
	\item Evaluation of Spoofax
\end{enumerate}
\end{frame}

@@

\begin{frame}[fragile]{Conclusions}
	\begin{itemize}
		\item \textbf{Spoofax perspective:} Support for complex inference could be improved, for example using equational unification.
		\item \textbf{Dependent types perspective:} This already functions as a great tool for prototyping dependently typed languages!
		% - Higher order 
	\end{itemize}
\end{frame}

>>>>

\begin{frame}[fragile]{Table of Contents}
	\begin{itemize}
		\item Background
		\item Why is this important?
		\item \textbf{Primary Contribution:} Calculus of Constructions
		\item Extensibility
		\item Comparison with implementation in Haskell
		\item Inference
	\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Extra contributions}
	% Refer to thesis for this
Features
\begin{enumerate}
	\item \textbf{Implemented Inference}
	\item Implemented Inductive Data Types
	\item Implemented Universes
	\item Interpreter
	\item Compiler to Clojure
\end{enumerate}
Evaluation
\begin{enumerate}
	\item \textbf{Comparison with implementation in Haskell}
	\item Comparison with implementation in LambdaPi
	\item Evaluation of Spoofax
\end{enumerate}
\end{frame}

@@

\begin{frame}[fragile]{Conclusions}
	\begin{itemize}
		\item Statix is already as a great tool for prototyping dependently typed languages!
		\item Support for complex inference could be improved, for example using equational unification.
	\end{itemize}
\end{frame}
